Constrained ordination method as a tool for performing genome scan and environmental genomic studies

### 2017-01-30 article_genome_scan.tex
Add files via upload
first update
typo

\author[Bazin et al.]{Eric \surname{Bazin},$^{\ast,1}$ Michael G. B.
Blum,$^{2}$}

@@

Results summarized on Fig \ref{fig:performance} is confirming that both methods have a good control of false discovery rate ($8.36 \times 10^{-2}$ for pcadapt and $8.51 \times 10^{-2}$ for RDA) and that overall RDA shows better performance at detecting true outliers since it succeeds to detect quite often QTL1 and QTL3 SNPs. It seems however less efficient at detecting QTL3 outliers but this might be due to the fact that local adaptation on a coarse environment is more difficult  that adaptation on a smooth environmental gradient as environment 1 and 2. These simulations plead in favor of using constrained ordination method instead of PCA when non genetic data such as environmental variable are available in order to orientate the axis in the direction of informative gradients.

@@

\bibliographystyle{natbib}%%%%natbib.sty
\bibliography{/Users/ericpbazin/Documents/BibTex/Article_ca_gs}%%%refs.bib

>>>>

\author[Bazin et al.]{Eric \surname{Bazin},$^{\ast,1}$ Keurcien Luu,$^{2}$ Michael G. B.
Blum,$^{2}$}

@@

Both methods have a good control of false discovery rate ($8.36 \times 10^{-2}$ for pcadapt and $8.51 \times 10^{-2}$ for RDA). Results summarized on Fig \ref{fig:performance} is confirming that overall RDA shows better performance at detecting true outliers since it succeeds to detect quite often QTL1 and QTL3 SNPs. It seems however less efficient at detecting QTL3 outliers but this might be due to the fact that local adaptation on a coarse environment is more difficult  that adaptation on a smooth environmental gradient as environment 1 and 2. These simulations plead in favor of using constrained ordination method instead of PCA when non genetic data such as environmental variable are available in order to orientate the axis in the direction of informative gradients.

@@

\bibliographystyle{natbib}%%%%natbib.sty
\bibliography{Article_ca_gs}%%%refs.bib
